### 2021-01-19 manuscript.tex
created yaml figs as images; improved fig description copy

% Packages and some formatting
\usepackage{titlesec,hyperref,booktabs,relsize,setspace,float,verbatim,caption,subcaption,graphicx}
%\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\hypersetup{hidelinks}
\titleformat{\chapter}[hang]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter:}{1em}{}
\doublespacing{}
\setcounter{tocdepth}{1}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{fig/rmarkdown_flow.png}
    \caption{Rmarkdown Rendering Flow}\label{fig:renderFlow}
\end{figure}

[render diagram https://rmarkdown.rstudio.com/lesson-2.html]

@@

\begin{figure}
\centering
    \addtolength\tabcolsep{-0.2em}
    \relsize{-2}
\begin{subfigure}[b]{.5\linewidth}
    \centering
\begin{verbatim}
name: "Candidate Cancer Gene Database"
navbar:
    title: "CCGD"
    left:
        - text: "Home"
          href: index.html
        - text: "Search"
          href: search.html
        - text: "Help"
          href: help.html
        - text: "References"
          href: references.html
        - text: "Contact"
          href: contact.html
\end{verbatim}
\caption{\_site.yml: file for site assembly}\label{fig:siteYaml}
\end{subfigure}%
\begin{subfigure}[b]{.5\textwidth}
\centering
\begin{verbatim}
---
title: "Candidate Cancer Gene Database"
bibliography: refs/ccgd_paper.bib
nocite: '@*'
output:
    html_document:
        includes:
            in_header: "styles/favicon.html"
            after_body: "styles/footer.html"
        css: styles/styles.css
        theme: readable
---
\end{verbatim}
\subcaption{index.Rmd individual page header}\label{fig:pageHeader}
\end{subfigure}
\caption{YAML Configuration Segments}\label{fig:yamls}
    \addtolength\tabcolsep{+0.2em}
    \relsize{+2}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/reactive_graph.png}
    \caption{table\_app/app.R Reactive Graph}\label{fig:reactiveGraph}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/parse_flow.png}
    \caption{Project directory file tree comparison}\label{fig:parseFlow}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/file_tree.png}
    \caption{Project directory file tree comparison}\label{fig:fileTree}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/space_tree.png}
    \caption{Treemap of Disk Use Between App Versions}\label{fig:spaceTree}
\end{figure}

>>>>

% Packages
\usepackage{titlesec,hyperref,booktabs,relsize,setspace,float,verbatim,caption,subcaption,graphicx}
%\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\hypersetup{hidelinks}
\titleformat{\chapter}[hang]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter:}{1em}{}
\setcounter{tocdepth}{1}

% Formatting
\doublespacing{}
%\setlength{\textfloatsep}{30pt plus 2.0pt minus 4.0pt}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{fig/rmarkdown_flow.png}
    \caption[Rmarkdown Rendering Flow]{\textbf{Rmarkdown Rendering Flow} The core web framework was created using a stitch process composed of two document conversion steps, which are both contained in the single \texttt{rmarkdow::render\_site} command. These two transformations are done by the R-specific knitr package and then the open-source pandoc tool. The first phase holds less relevance in particular as its role is to execute R code chunks, of which there are few in our site content. The markdown output from this step is seamlessly injected into a pandoc conversion which offers a large variety in document output. Specific to our case, the pandoc conversion paired with a companion yaml configuration file allows for multidocument markdown-to-html rendering which is assembled as a complete site stack. As a single process, this function generates an integrated, modern web front-end from content written in a light-weight syntax with almost none of the typical complexity of full-scale web page creation.}\label{fig:renderFlow}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/page_header.png}
\subcaption{index.Rmd individual page header}\label{fig:pageHeader}
\end{subfigure}%
\hspace{5em}
\begin{subfigure}[t]{.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/site_header.png}
\caption{\_site.yml: file for site assembly}\label{fig:siteYaml}
\end{subfigure}
\caption[YAML Configuration Segments]{\textbf{YAML Configuration Segments} Pictured above are the two forms of complete yaml configuration headers utilized in Rmarkdown rendering. The central takeaway from this illustration is to recognize the heavy lifting performed by these relatively small code segments. Figure~\ref{fig:pageHeader} provides an example of the header found in every~.Rmd file that make-up the respective pages of the site. These headers provide primarily formatting configuration for the rendering process but include broader functions as well. The header can be as simple as listing a title and pandoc output type or include LaTex bibliography functionality and read-in style sheets like the one shown. Either way, a few lines of configuration generate wildly different outputs. Figure~\ref{fig:siteYaml} presents the yaml file which serves to assemble independent Rmarkdown files into a joined website as described in figure~\ref{fig:renderFlow}. There is less configuration here as the only real purpose is to define the site tree for the \texttt{rmarkdown::render\_site} process.}\label{fig:yamls}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/reactive_graph.png}
    \caption[\texttt{table\_app/app.R} Reactive Graph]{\textbf{\texttt{table\_app/app.R} Reactive Graph} An Rshiny app design can be defined by its reactive graph. The graph above displays the process flow of our app by highlighting modularity in the data streams around the table filtering process. The reactive web design is intended to allow for the automatic implementation of changed states applied through the alternate paths of the graph. This allows for the passive display of a static representation of the table while allowing for dynamic adjustment to filtering inputs through the \texttt{[Var] $\rightarrow$ [Var].values} path. Additionally, this declarative model provides for an interactive table array while only drawing computation when the appropriate event is called.}\label{fig:reactiveGraph}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/parse_flow.png}
    \caption[Server-side Processing Flow]{\textbf{Server-side Processing Flow} This diagram illustrates a small but fundamental change applied to the application table processing through the lens of the server-client relationship. The ``old'' flow shows the prior table processing procedure, which is highly typical of a classic Linux-Apache-MySql-PHP (LAMP) stack website. Inputs and calls made by the browser occur from and within a client-side rendering engine which delivers a static request to the server-side SQL database. The database returns parsed XML to the browser that is rendered and displayed. Our fundamental shift was to move this data processing entirely to JavaScript. Typically, this would result in client-side processing that would prohibit large tables like ours. Instead, we leveraged a server-side engine to handle asynchronous AJAX requests which are returned with parsed JSON, shown in the ``new'' path. This processing flow allows for the use of a single~.csv file as the data source in table presentation, ordering, and pagination, ultimately eliminating the need for a SQL architecture.}\label{fig:parseFlow}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/file_tree.png}
    \caption[Project Directory File Tree Comparison]{\textbf{Project Directory File Tree Comparison} The above figure offers a qualitative assessment of an element of technical debt that was improved in refactoring. Shown are the file trees of the site directories of the new and old projects. What is illustrated is a dramatic improvement in the tree size and complexity through the elimination of a large degree of content, log, and style files. This is accentuated even forther when comparing the source code. This was accomplished both in the intentional design of eliminating content redundancy and in the streamlined structure of the Rmarkdown rendering process. This allowed for the elimination of several dimensions of broader web design elements.}\label{fig:fileTree}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/space_tree.png}
    \caption{Disk Use Comparison}\label{fig:spaceTree}
\end{figure}
